Accra - process flow

### 2018-07-09 doc/accra/process_flow.rmd
Formatting
Remove a repeated word

Leandro has already removed >70 population from it
This has people without trips (trip_mode 99 and trip_id 0) as well

@@

* Scenario 1: Shift modes - 50% of all walking walking trips to Private Car

>>>>

Leandro has already removed >70 population from it

(this has people without trips (trip_mode 99 and trip_id 0) as well)

@@

* Scenario 1: Shift modes - 50% of all walking trips to Private Car
